---
title: "`r params$rmd_title`"
author: "Universidad de Deusto (carlos.quesada@deusto.es)"
date: "`r format(Sys.time())`"
output:
  html_document:
  toc: true
toc_depth: 1
theme: united
params:
  rmd_title: "Cluster Report"
  no_cards: 1650
  no_card_types: 33
  card_width: "300px"
  hmp_dir:   ""
  distr_dir: ""
  acf_dir:   ""
  dplot_dir: "" 
  nofile_path: "no-file.png"
  ff: ""
  dd: ""
  mm: ""
  cc: ""
---

```{css, echo=FALSE}
.main-container {
    max-width: 100%;
    margin-left: auto;
    margin-right: auto;
}
```

<hr>
  
#### List of abbreviations
  
##### Sets of features 
* __sAggrDRM__: seasonal aggregates v2.0 (day-referenced mean)
* __sAggrP6__: seasonal aggregates v3.0 (6-period time division)

##### Datasets
* __edrp__: Energy Demand Research Project (EDRP) [GB]
* __goi__: GoiEner (including Megara and La Corriente) [ES]
* __iss__: Irish Social Science Data Archive (ISSDA) [IE]
* __lcl__: Low Carbon London [GB]
* __nee__: Northwest Energy Efficiency Alliance (NEEA) [US]
* __por__: Elergone Energia [PT]
* __Xds__: X datasets put together

##### Clustering methods
* __kme__: _k_-means
* __pam__: partition around medoids
* __som__: self-organizing maps

##### Statistic used
* __m__: mean
* __sd__: standard deviation
* __rsd__: relative standard deviation

<hr>

```{r, include=FALSE}
# CARD TYPES
### MEANS
# card_types_p <- c(
#   "kp1_", "kp2_", "kp3_",
#   paste0(c(rep("dp1_",9), rep("dp2_",9), rep("dp3_",9)), 1:9, "_"),
#   "ap1_", "ap2_", "ap3_"
# )
### MEDIANS
card_types_p <- c(
  "kp4_", "kp5_", "kp6_",
  paste0(c(rep("dp4_",9), rep("dp5_",9), rep("dp6_",9)), 1:9, "_"),
  "ap4_", "ap5_", "ap6_"
)
card_types_m <- c(
  rep("hd_",3),
  rep("dd_",27),
  rep(NA,3)
)
# stat_vect <- c("mean", "sd", "cvar")
stat_vect <- c("median", "mad", "rmad")
distr_vect <- c(
  "unif", "norm", "lnorm", "exp", "cauchy", "gamma", "logis", "weibull", "sgt"
)
card_types_c <- c(
  paste("hmp", stat_vect, sep="_"),
  paste(rep(stat_vect,each=9), rep(distr_vect,3), sep="_"),
  paste("acf", stat_vect, sep="_")
)
# Paths to graphs
p_path <- c(
  rep(params$hmp_dir, 3),
  rep(params$distr_dir, 27),
  rep(params$acf_dir, 3)
)
# Paths to values
m_path <- c(
  rep(params$dplot_dir, 30),
  rep(NA, 3) 
)
# No file by DEFAULT
no_file <- paste0("![](", params$nofile_path, ")")

# Block of cards ("bb" is an integer indicating the desired number of blocks)
block_of_cards <- function(txt_list, blocks, elems, card_width){
  o <- ""
  for (bb in 1:blocks) {
    # PART 1
    o <- paste0(o,
'<tr>')
    for (ee in 1:elems) {
      o <- paste0(o,
'<td width="', card_width, '">', txt_list$img[elems*bb-(elems-ee)], '</td>')
    }
    o <- paste0(o,
'</tr>')
    # PART 2
    o <- paste0(o,
'<tr>')
    for (ee in 1:elems) {
      o <- paste0(o,
'<td><center><small>', txt_list$cap[elems*bb-(elems-ee)], '</small></center></td>')
    }
    o <- paste0(o,
'</tr>')
  }
  return(o)
}

# Table of cards
table_of_cards <- function(txt_list) {
  boc <- block_of_cards(
    txt_list,
    ceiling(params$no_cards/params$no_card_types),
    params$no_card_types,
    params$card_width
  )
  o <- paste0(
'<table border="0" style="width:800%">
', boc,
'</table>\n\n
'
  )
  return(o)
}
```

```{r, echo=FALSE, results='asis', message=FALSE}
# Features loop
ff_loop <- params$ff
# Dataset loop
key     <- unique(sapply(1:length(params$dd),
                           function(x) params$dd[[x]]$key))
len_key <- length(key)
dd_name <- ifelse(len_key == 1, key, paste0(len_key, "ds"))
dd_loop <- dd_name
# Methods loop
mm_loop <- params$mm
# FEATURE LOOP
for (ff in ff_loop) {
  # DATASET LOOP
  for (dd in dd_loop) {
    # METHOD LOOP
    for (mm in mm_loop) {
      # cat(paste0("#### ", ff, " > ", dd, " > ", mm, "\n\n"))
      # Initialization of txt_list
      txt_list <- list(
        img = rep("", params$no_cards),
        cap = rep("", params$no_cards)
      )
      # CLUSTER LOOP
      cc_loop <- 1:params$cc
      
      for (cc in cc_loop) {
        for (xx in 1:params$no_card_types) {
          # Path to file
          card_path <- paste0(
            p_path[xx], card_types_p[xx], ff, "_", dd, "_", mm, "_",
            max(cc_loop), "cl_i-", cc, ".png"
          )
          # Path for loading variable "idx"
          idx_path <- paste0(
            m_path[xx], card_types_m[xx], ff, "_", dd, "_", mm, "_",
            max(cc_loop), "cl_i-", cc, ".RData"
          )
          # This loads variable "idx"
          if (xx %in% 1:3) {
            if (file.exists(idx_path)) {
              load(idx_path)  
              sum_idx <- sum(idx)
              pct_idx <- round(100*sum(idx)/length(idx),1)
            } else {
              sum_idx <- "?"
              pct_idx <- "?"
            }
          }
          if (xx %in% 4:30) {
            if (file.exists(idx_path)) {
              load(idx_path) 
              idx1 <- (xx-4) %/% 9 + 1
              idx2 <- (xx-4) %% 9 + 1
              loglik <- d[[idx1]][[idx2]]$loglik
              aic    <- d[[idx1]][[idx2]]$aic
              bic    <- d[[idx1]][[idx2]]$bic
              loglik <- ifelse(is.null(loglik), "?", round(loglik))
              aic    <- ifelse(is.null(aic), "?", round(aic))
              bic    <- ifelse(is.null(bic), "?", round(bic))
            } else {
              loglik <- "?"
              aic    <- "?"
              bic    <- "?"
            }
          }
          # Complete txt_list
          card_idx <- params$no_card_types*cc - (params$no_card_types-xx)
          if (file.exists(card_path)) {
            txt_list$img[card_idx] <- paste0("![](", card_path, ")")
          } else {
            txt_list$img[card_idx] <- no_file
          }
          if (xx %in% 1:3) {
            txt_list$cap[card_idx] <- paste0(
              ff, " > ", dd, " > ", mm, " > ", card_types_c[xx], 
              " > #", cc, "\n\n", sum_idx, " TS (", pct_idx, "%)\n\n"
            )
          }
          if (xx %in% 4:30) {
            txt_list$cap[card_idx] <- paste0(
              ff, " > ", dd, " > ", mm, " > ", card_types_c[xx], 
              " > #", cc, "\n\n", "loglik = ", loglik, " | aic = ", aic, 
              " | bic = ", bic
            )
          }
          if (xx %in% 31:33) {
            txt_list$cap[card_idx] <- paste0(
              ff, " > ", dd, " > ", mm, " > ", card_types_c[xx], " > #", cc
            )
          }
        }
        
        # Print HTML table
        if (cc == max(cc_loop)) {
          cat(table_of_cards(txt_list))
        }
      }
    }
  }
}
```