---
title: "`r params$rmd_title`"
author: "Universidad de Deusto (carlos.quesada@deusto.es)"
date: "`r format(Sys.time())`"
output:
  html_document:
  toc: true
toc_depth: 1
theme: united
params:
  rmd_title: "Cluster Report"
  hmp_dir: ""
  hmm_dir: ""
  hmpsd_dir: ""
  hmmsd_dir: ""
  nofile_path: "no-file.png"
  ff: ""
  dd: ""
  mm: ""
  cc: ""
---

<style type="text/css">
  .main-container {
    max-width: 100%;
    margin-left: auto;
    margin-right: auto;
  }
</style>

<hr>
  
#### List of abbreviations
  
##### Sets of features 
* __sAggrDRM__: seasonal aggregates v2.0 (day-referenced mean)
* __sAggrP6__: seasonal aggregates v3.0 (6-period time division)

##### Datasets
* __goi__: GoiEner (including Megara and La Corriente) [ES]
* __lcl__: Low Carbon London [GB]
* __iss__: Irish Social Science Data Archive (ISSDA) [IE]
* __por__: Elergone Energia [PT]
* __nee__: Northwest Energy Efficiency Alliance (NEEA) [US]
* __Nds__: N datasets put together

##### Clustering methods
* __som__: self-organizing maps

##### Statistic used
* __μ__: mean
* __σ__: standard deviation


<hr>


```{r, include=FALSE}
# Path to hmp graphs
hmp_path <- params$hmp_dir
# Path to hmm values
hmm_path <- params$hmm_dir
# Path to hmp graphs
hmpsd_path <- params$hmpsd_dir
# Path to hmm values
hmmsd_path <- params$hmmsd_dir
# No file by DEFAULT
no.file_path  <- params$nofile_path
no_file <- paste0("![](", no.file_path, ")")
# Table of cards
table_of_cards <- function(txt_list) {
  o <- paste0(
'<table border="0">
<tr>
<td width="16.66%">', txt_list$img[1], '</td>
<td width="16.66%">', txt_list$img[2], '</td>
<td width="16.66%">', txt_list$img[3], '</td>
<td width="16.66%">', txt_list$img[4], '</td>
<td width="16.66%">', txt_list$img[5], '</td>
<td width="16.66%">', txt_list$img[6], '</td>
</tr>
<tr>
<td><center><small>', txt_list$cap[1], '</small></center></td>
<td><center><small>', txt_list$cap[2], '</small></center></td>
<td><center><small>', txt_list$cap[3], '</small></center></td>
<td><center><small>', txt_list$cap[4], '</small></center></td>
<td><center><small>', txt_list$cap[5], '</small></center></td>
<td><center><small>', txt_list$cap[6], '</small></center></td>
</tr>
<tr>
<td>', txt_list$img[7], '</td>
<td>', txt_list$img[8], '</td>
<td>', txt_list$img[9], '</td>
<td>', txt_list$img[10], '</td>
<td>', txt_list$img[11], '</td>
<td>', txt_list$img[12], '</td>
</tr>
<tr>
<td><center><small>', txt_list$cap[7], '</small></center></td>
<td><center><small>', txt_list$cap[8], '</small></center></td>
<td><center><small>', txt_list$cap[9], '</small></center></td>
<td><center><small>', txt_list$cap[10], '</small></center></td>
<td><center><small>', txt_list$cap[11], '</small></center></td>
<td><center><small>', txt_list$cap[12], '</small></center></td>
</tr>
<tr>
<td>', txt_list$img[13], '</td>
<td>', txt_list$img[14], '</td>
<td>', txt_list$img[15], '</td>
<td>', txt_list$img[16], '</td>
<td>', txt_list$img[17], '</td>
<td>', txt_list$img[18], '</td>
</tr>
<tr>
<td><center><small>', txt_list$cap[13], '</small></center></td>
<td><center><small>', txt_list$cap[14], '</small></center></td>
<td><center><small>', txt_list$cap[15], '</small></center></td>
<td><center><small>', txt_list$cap[16], '</small></center></td>
<td><center><small>', txt_list$cap[17], '</small></center></td>
<td><center><small>', txt_list$cap[18], '</small></center></td>
</tr>
<tr>
<td>', txt_list$img[19], '</td>
<td>', txt_list$img[20], '</td>
<td>', txt_list$img[21], '</td>
<td>', txt_list$img[22], '</td>
<td>', txt_list$img[23], '</td>
<td>', txt_list$img[24], '</td>
</tr>
<tr>
<td><center><small>', txt_list$cap[19], '</small></center></td>
<td><center><small>', txt_list$cap[20], '</small></center></td>
<td><center><small>', txt_list$cap[21], '</small></center></td>
<td><center><small>', txt_list$cap[22], '</small></center></td>
<td><center><small>', txt_list$cap[23], '</small></center></td>
<td><center><small>', txt_list$cap[24], '</small></center></td>
</tr>
<tr>
<td>', txt_list$img[25], '</td>
<td>', txt_list$img[26], '</td>
<td>', txt_list$img[27], '</td>
<td>', txt_list$img[28], '</td>
<td>', txt_list$img[29], '</td>
<td>', txt_list$img[30], '</td>
</tr>
<tr>
<td><center><small>', txt_list$cap[25], '</small></center></td>
<td><center><small>', txt_list$cap[26], '</small></center></td>
<td><center><small>', txt_list$cap[27], '</small></center></td>
<td><center><small>', txt_list$cap[28], '</small></center></td>
<td><center><small>', txt_list$cap[29], '</small></center></td>
<td><center><small>', txt_list$cap[30], '</small></center></td>
</tr>
<tr>
<td>', txt_list$img[31], '</td>
<td>', txt_list$img[32], '</td>
<td>', txt_list$img[33], '</td>
<td>', txt_list$img[34], '</td>
<td>', txt_list$img[35], '</td>
<td>', txt_list$img[36], '</td>
</tr>
<tr>
<td><center><small>', txt_list$cap[31], '</small></center></td>
<td><center><small>', txt_list$cap[32], '</small></center></td>
<td><center><small>', txt_list$cap[33], '</small></center></td>
<td><center><small>', txt_list$cap[34], '</small></center></td>
<td><center><small>', txt_list$cap[35], '</small></center></td>
<td><center><small>', txt_list$cap[36], '</small></center></td>
</tr>
<tr>
<td>', txt_list$img[37], '</td>
<td>', txt_list$img[38], '</td>
<td>', txt_list$img[39], '</td>
<td>', txt_list$img[40], '</td>
<td>', txt_list$img[41], '</td>
<td>', txt_list$img[42], '</td>
</tr>
<tr>
<td><center><small>', txt_list$cap[37], '</small></center></td>
<td><center><small>', txt_list$cap[38], '</small></center></td>
<td><center><small>', txt_list$cap[39], '</small></center></td>
<td><center><small>', txt_list$cap[40], '</small></center></td>
<td><center><small>', txt_list$cap[41], '</small></center></td>
<td><center><small>', txt_list$cap[42], '</small></center></td>
</tr>
<tr>
<td>', txt_list$img[43], '</td>
<td>', txt_list$img[44], '</td>
<td>', txt_list$img[45], '</td>
<td>', txt_list$img[46], '</td>
<td>', txt_list$img[47], '</td>
<td>', txt_list$img[48], '</td>
</tr>
<tr>
<td><center><small>', txt_list$cap[43], '</small></center></td>
<td><center><small>', txt_list$cap[44], '</small></center></td>
<td><center><small>', txt_list$cap[45], '</small></center></td>
<td><center><small>', txt_list$cap[46], '</small></center></td>
<td><center><small>', txt_list$cap[47], '</small></center></td>
<td><center><small>', txt_list$cap[48], '</small></center></td>
</tr>
<tr>
<td>', txt_list$img[49], '</td>
<td>', txt_list$img[50], '</td>
<td>', txt_list$img[51], '</td>
<td>', txt_list$img[52], '</td>
<td>', txt_list$img[53], '</td>
<td>', txt_list$img[54], '</td>
</tr>
<tr>
<td><center><small>', txt_list$cap[49], '</small></center></td>
<td><center><small>', txt_list$cap[50], '</small></center></td>
<td><center><small>', txt_list$cap[51], '</small></center></td>
<td><center><small>', txt_list$cap[52], '</small></center></td>
<td><center><small>', txt_list$cap[53], '</small></center></td>
<td><center><small>', txt_list$cap[54], '</small></center></td>
</tr>
<tr>
<td>', txt_list$img[55], '</td>
<td>', txt_list$img[56], '</td>
<td>', txt_list$img[57], '</td>
<td>', txt_list$img[58], '</td>
<td>', txt_list$img[59], '</td>
<td>', txt_list$img[60], '</td>
</tr>
<tr>
<td><center><small>', txt_list$cap[55], '</small></center></td>
<td><center><small>', txt_list$cap[56], '</small></center></td>
<td><center><small>', txt_list$cap[57], '</small></center></td>
<td><center><small>', txt_list$cap[58], '</small></center></td>
<td><center><small>', txt_list$cap[59], '</small></center></td>
<td><center><small>', txt_list$cap[60], '</small></center></td>
</tr>
<tr>
<td>', txt_list$img[61], '</td>
<td>', txt_list$img[62], '</td>
<td>', txt_list$img[63], '</td>
<td>', txt_list$img[64], '</td>
<td>', txt_list$img[65], '</td>
<td>', txt_list$img[66], '</td>
</tr>
<tr>
<td><center><small>', txt_list$cap[61], '</small></center></td>
<td><center><small>', txt_list$cap[62], '</small></center></td>
<td><center><small>', txt_list$cap[63], '</small></center></td>
<td><center><small>', txt_list$cap[64], '</small></center></td>
<td><center><small>', txt_list$cap[65], '</small></center></td>
<td><center><small>', txt_list$cap[66], '</small></center></td>
</tr>
<tr>
<td>', txt_list$img[67], '</td>
<td>', txt_list$img[68], '</td>
<td>', txt_list$img[69], '</td>
<td>', txt_list$img[70], '</td>
<td>', txt_list$img[71], '</td>
<td>', txt_list$img[72], '</td>
</tr>
<tr>
<td><center><small>', txt_list$cap[67], '</small></center></td>
<td><center><small>', txt_list$cap[68], '</small></center></td>
<td><center><small>', txt_list$cap[69], '</small></center></td>
<td><center><small>', txt_list$cap[70], '</small></center></td>
<td><center><small>', txt_list$cap[71], '</small></center></td>
<td><center><small>', txt_list$cap[72], '</small></center></td>
</tr>
<tr>
<td>', txt_list$img[73], '</td>
<td>', txt_list$img[74], '</td>
<td>', txt_list$img[75], '</td>
<td>', txt_list$img[76], '</td>
<td>', txt_list$img[77], '</td>
<td>', txt_list$img[78], '</td>
</tr>
<tr>
<td><center><small>', txt_list$cap[73], '</small></center></td>
<td><center><small>', txt_list$cap[74], '</small></center></td>
<td><center><small>', txt_list$cap[75], '</small></center></td>
<td><center><small>', txt_list$cap[76], '</small></center></td>
<td><center><small>', txt_list$cap[77], '</small></center></td>
<td><center><small>', txt_list$cap[78], '</small></center></td>
</tr>
<tr>
<td>', txt_list$img[79], '</td>
<td>', txt_list$img[80], '</td>
<td>', txt_list$img[81], '</td>
<td>', txt_list$img[82], '</td>
<td>', txt_list$img[83], '</td>
<td>', txt_list$img[84], '</td>
</tr>
<tr>
<td><center><small>', txt_list$cap[79], '</small></center></td>
<td><center><small>', txt_list$cap[80], '</small></center></td>
<td><center><small>', txt_list$cap[81], '</small></center></td>
<td><center><small>', txt_list$cap[82], '</small></center></td>
<td><center><small>', txt_list$cap[83], '</small></center></td>
<td><center><small>', txt_list$cap[84], '</small></center></td>
</tr>
</table>\n\n'
)
  return(o)
}
```

```{r, echo=FALSE, results='asis', message=FALSE}
# Features loop
ff_loop <- params$ff
# Dataset loop
key     <- unique(unlist(lapply(params$dd, `[[`, 1)))
len_key <- length(key)
dd_name <- ifelse(len_key == 1, key, paste0(len_key, "ds")) 
dd_loop <- dd_name
# Methods loop
mm_loop <- params$mm
# FEATURE LOOP
for (ff in ff_loop) {
  # DATASET LOOP
  for (dd in dd_loop) {
    # METHOD LOOP
    for (mm in mm_loop) {
      cat(paste0("## ", ff, " > ", dd, " > ", mm, "\n\n"))
      # Initialization of txt_list
      txt_list <- list(img = rep("", 84), cap = rep("", 84))
      # CLUSTER LOOP
      cc_loop <- 1:params$cc
      
      for (cc in cc_loop) {
        # Path to file
        card_path <- paste0(hmp_path, "hmp_", ff, "_", dd, "_", mm, "_",
                            max(cc_loop), "cl_i-", cc, ".png")
        # Load variable "idx"
        idx_path <- paste0(hmm_path, "hmm_", ff, "_", dd, "_", mm, "_",
                            max(cc_loop), "cl_i-", cc, ".RData")
        load(idx_path)
        
        # Complete txt_list (MEAN)
        if (file.exists(card_path)) {
          txt_list$img[2*cc-1] <- paste0("![](", card_path, ")")
        } else {
          txt_list$img[2*cc-1] <- no_file
        }
        txt_list$cap[2*cc-1] <- paste0(
          ff, " > ", 
          dd, " > ", 
          mm, " > ",
          "μ > #", cc, "\n\n",
          sum(idx), " TS (", round(100*sum(idx)/length(idx),1), "%)\n\n"
        )
        
        # Path to file
        card_path <- paste0(hmpsd_path, "hmpsd_", ff, "_", dd, "_", mm, "_",
                            max(cc_loop), "cl_i-", cc, ".png")
        # Load variable "idx"
        idx_path <- paste0(hmmsd_path, "hmmsd_", ff, "_", dd, "_", mm, "_",
                            max(cc_loop), "cl_i-", cc, ".RData")
        load(idx_path)
        
        # Complete txt_list (SD)
        if (file.exists(card_path)) {
          txt_list$img[2*cc] <- paste0("![](", card_path, ")")
        } else {
          txt_list$img[2*cc] <- no_file
        }
        txt_list$cap[2*cc] <- paste0(
          ff, " > ", 
          dd, " > ", 
          mm, " > ", 
          "σ > #", cc, "\n\n",
          sum(idx), " TS (", round(100*sum(idx)/length(idx),1), "%)\n\n"
        )
        
        # Print HTML table
        if (cc == max(cc_loop)) {
          cat(table_of_cards(txt_list))
        }
      }
    }
  }
}
```