---
title: "`r params$rmd_title`"
author: "Universidad de Deusto (carlos.quesada@deusto.es)"
date: "`r format(Sys.time())`"
output:
  html_document:
  toc: true
toc_depth: 1
theme: united
params:
  rmd_title: "Cluster Report"
  no_cards: 120
  no_card_types: 3
  hmp_dir: ""
  hmm_dir: ""
  hmpsd_dir: ""
  hmmsd_dir: ""
  hmprsd_dir: ""
  hmmrsd_dir: ""
  nofile_path: "no-file.png"
  ff: ""
  dd: ""
  mm: ""
  cc: ""
---

<style type="text/css">
  .main-container {
    max-width: 100%;
    margin-left: auto;
    margin-right: auto;
  }
</style>

<hr>
  
#### List of abbreviations
  
##### Sets of features 
* __sAggrDRM__: seasonal aggregates v2.0 (day-referenced mean)
* __sAggrP6__: seasonal aggregates v3.0 (6-period time division)

##### Datasets
* __goi__: GoiEner (including Megara and La Corriente) [ES]
* __lcl__: Low Carbon London [GB]
* __iss__: Irish Social Science Data Archive (ISSDA) [IE]
* __por__: Elergone Energia [PT]
* __nee__: Northwest Energy Efficiency Alliance (NEEA) [US]
* __Nds__: N datasets put together

##### Clustering methods
* __kme__: _k_-means
* __pam__: partition around medoids
* __som__: self-organizing maps

##### Statistic used
* __μ__: mean
* __σ__: standard deviation
* __σ/μ__: relative standard deviation

<hr>

```{r, include=FALSE}
# CARD TYPES
card_types_p <- c("hmp_", "hmpsd_", "hmprsd_")
card_types_m <- c("hmm_", "hmmsd_", "hmmrsd_")
card_types_c <- c("μ", "σ", "σ/μ")
# Path to hmp graphs
p_path <- c(params$hmp_dir, params$hmpsd_dir, params$hmprsd_dir)
# Path to hmm values
m_path <- c(params$hmm_dir, params$hmmsd_dir, params$hmmrsd_dir)
# No file by DEFAULT
no_file <- paste0("![](", params$nofile_path, ")")

# Block of cards ("bb" is an integer indicating the desired number of blocks)
block_of_cards <- function(txt_list, blocks){
  o <- ""
  for (bb in 1:blocks) {
    o <- paste0(o,
'<tr>
<td width="16.66%">', txt_list$img[6*bb-5], '</td>
<td width="16.66%">', txt_list$img[6*bb-4], '</td>
<td width="16.66%">', txt_list$img[6*bb-3], '</td>
<td width="16.66%">', txt_list$img[6*bb-2], '</td>
<td width="16.66%">', txt_list$img[6*bb-1], '</td>
<td width="16.66%">', txt_list$img[6*bb], '</td>
</tr>
<tr>
<td><center><small>', txt_list$cap[6*bb-5], '</small></center></td>
<td><center><small>', txt_list$cap[6*bb-4], '</small></center></td>
<td><center><small>', txt_list$cap[6*bb-3], '</small></center></td>
<td><center><small>', txt_list$cap[6*bb-2], '</small></center></td>
<td><center><small>', txt_list$cap[6*bb-1], '</small></center></td>
<td><center><small>', txt_list$cap[6*bb], '</small></center></td>
</tr>
'
    )
  }
  return(o)
}

# Table of cards
table_of_cards <- function(txt_list) {
  boc <- block_of_cards(txt_list, ceiling(params$no_cards/6))
  message(txt_list$img)
  o <- paste0(
'<table border="0">
', boc,
'</table>\n\n
'
  )
  return(o)
}
```

```{r, echo=FALSE, results='asis', message=FALSE}
# Features loop
ff_loop <- params$ff
# Dataset loop
key     <- unique(sapply(1:length(params$dd),
                           function(x) params$dd[[x]]$key))
len_key <- length(key)
dd_name <- ifelse(len_key == 1, key, paste0(len_key, "ds"))
dd_loop <- dd_name
# Methods loop
mm_loop <- params$mm
# FEATURE LOOP
for (ff in ff_loop) {
  # DATASET LOOP
  for (dd in dd_loop) {
    # METHOD LOOP
    for (mm in mm_loop) {
      cat(paste0("## ", ff, " > ", dd, " > ", mm, "\n\n"))
      # Initialization of txt_list
      txt_list <- list(
        img = rep("", params$no_cards),
        cap = rep("", params$no_cards)
      )
      # CLUSTER LOOP
      cc_loop <- 1:params$cc
      
      for (cc in cc_loop) {
        for (xx in 1:params$no_card_types) {
          # Path to file
          card_path <- paste0(
            p_path[xx], card_types_p[xx], ff, "_", dd, "_", mm, "_",
            max(cc_loop), "cl_i-", cc, ".png"
          )
          # Path for loading variable "idx"
          idx_path <- paste0(
            m_path[xx], card_types_m[xx], ff, "_", dd, "_", mm, "_",
            max(cc_loop), "cl_i-", cc, ".RData"
          )
          # This loads varible "idx"
          if (file.exists(idx_path)) {
            load(idx_path)  
            sum_idx <- sum(idx)
            pct_idx <- round(100*sum(idx)/length(idx),1)
          } else {
            sum_idx <- "?"
            pct_idx <- "?"
          }
          # Complete txt_list
          card_idx <- params$no_card_types*cc - (params$no_card_types-xx)
          if (file.exists(card_path)) {
            txt_list$img[card_idx] <- paste0("![](", card_path, ")")
          } else {
            txt_list$img[card_idx] <- no_file
          }
          txt_list$cap[card_idx] <- paste0(
            ff, " > ", dd, " > ", mm, " > ", params$card_types_c[xx], 
            " > #", cc, "\n\n", sum_idx, " TS (", pct_idx, "%)\n\n"
          )
        }
        
        # Print HTML table
        if (cc == max(cc_loop)) {
          cat(table_of_cards(txt_list))
        }
      }
    }
  }
}
```