---
title: "Cluster Report v2.0 (executive summary)"
author: "Universidad de Deusto (carlos.quesada@deusto.es)"
date: "June 8, 2021"
output:
  html_document:
    toc: true
    toc_depth: 4
    theme: united
---

<style type="text/css">
.main-container {
  max-width: 100%;
  margin-left: auto;
  margin-right: auto;
}
</style>

#### List of abbreviations

##### Sets of features 
* __Seas.aggr.__: seasonal aggregates
* __(off)-Peaks__: peak and off-peak values
* __Strength/AC__: seasonal strengths and autocorrelations 
* __Catch-22__

##### Datasets
* __LCL__: Low Carbon London (GB)
* __ISS-hh__: ISSDA, only households (IE)
* __GOI-all__: GoiEner & Megara, all time series (ES)
* __POR__: UCI, Portugal (PT)
* __NEE__: NEEA, Western United States (US)
* __all__: all time series

##### Clustering methods
* __*k*-m__: *k*-means
* __SOM__: self-organizing maps

<!--
rmarkdown::render("G:/Mi unidad/WHY/Github/why-T2.1/_analyses/cards/cards_6x4.Rmd") 
-->

```{r, include=FALSE}

# Path to hmp graphs
hmp_path <- "G:/Mi unidad/WHY/Analyses/clValid2/2021.06.07_km-som-nodst/hmp/"

# No file by DEFAULT
no.file_path  <- "G:/Mi unidad/WHY/Github/why-T2.1/_analyses/no-file.png"
no_file <- paste0("![](", no.file_path, ")")

# Table of cards
table_of_cards <- function(txt_list) {
  o <- paste0(
    '<table border="0">
    <tr>
    <td width="16.66%">', txt_list$img[1], '</td>
    <td width="16.66%">', txt_list$img[2], '</td>
    <td width="16.66%">', txt_list$img[3], '</td>
    <td width="16.66%">', txt_list$img[4], '</td>
    <td width="16.66%">', txt_list$img[5], '</td>
    <td width="16.66%">', txt_list$img[6], '</td>
    </tr>
    <tr>
    <td><center><small>', txt_list$cap[1], '</small></center></td>
    <td><center><small>', txt_list$cap[2], '</small></center></td>
    <td><center><small>', txt_list$cap[3], '</small></center></td>
    <td><center><small>', txt_list$cap[4], '</small></center></td>
    <td><center><small>', txt_list$cap[5], '</small></center></td>
    <td><center><small>', txt_list$cap[6], '</small></center></td>
    </tr>
    <tr>
    <td>', txt_list$img[7], '</td>
    <td>', txt_list$img[8], '</td>
    <td>', txt_list$img[9], '</td>
    <td>', txt_list$img[10], '</td>
    <td>', txt_list$img[11], '</td>
    <td>', txt_list$img[12], '</td>
    </tr>
    <tr>
    <td><center><small>', txt_list$cap[7], '</small></center></td>
    <td><center><small>', txt_list$cap[8], '</small></center></td>
    <td><center><small>', txt_list$cap[9], '</small></center></td>
    <td><center><small>', txt_list$cap[10], '</small></center></td>
    <td><center><small>', txt_list$cap[11], '</small></center></td>
    <td><center><small>', txt_list$cap[12], '</small></center></td>
    </tr>
    <tr>
    <td>', txt_list$img[13], '</td>
    <td>', txt_list$img[14], '</td>
    <td>', txt_list$img[15], '</td>
    <td>', txt_list$img[16], '</td>
    <td>', txt_list$img[17], '</td>
    <td>', txt_list$img[18], '</td>
    </tr>
    <tr>
    <td><center><small>', txt_list$cap[13], '</small></center></td>
    <td><center><small>', txt_list$cap[14], '</small></center></td>
    <td><center><small>', txt_list$cap[15], '</small></center></td>
    <td><center><small>', txt_list$cap[16], '</small></center></td>
    <td><center><small>', txt_list$cap[17], '</small></center></td>
    <td><center><small>', txt_list$cap[18], '</small></center></td>
    </tr>
    <tr>
    <td>', txt_list$img[19], '</td>
    <td>', txt_list$img[20], '</td>
    <td>', txt_list$img[21], '</td>
    <td>', txt_list$img[22], '</td>
    <td>', txt_list$img[23], '</td>
    <td>', txt_list$img[24], '</td>
    </tr>
    <tr>
    <td><center><small>', txt_list$cap[19], '</small></center></td>
    <td><center><small>', txt_list$cap[20], '</small></center></td>
    <td><center><small>', txt_list$cap[21], '</small></center></td>
    <td><center><small>', txt_list$cap[22], '</small></center></td>
    <td><center><small>', txt_list$cap[23], '</small></center></td>
    <td><center><small>', txt_list$cap[24], '</small></center></td>
    </tr>
    </table>\n\n'
  )
  return(o)
}

# Set of features
feature_list <- c(
  "Seas.aggr.",
  "(off)-Peaks",
  "Strength/AC",
  "Catch-22"
)
# Datasets
dataset_list <- c(
  "GOI-hh",
  "LCL",
  "ISS-hh",
  "GOI-all",
  "POR",
  "NEE",
  "all"
)
# Clustering
method_list <- c(
  "Hierarch.",
  "*k*-m",
  "DIANA",
  "FANNY",
  "SOM",
  "PAM",
  "SOTA",
  "CLARA",
  "Model-based"
)

```

```{r, results='asis', echo=FALSE}

# Features loop
ff_loop <- 1:4
# Dataset loop
dd_loop <- 2:7
# Methods loop
mm_loop <- c(2,5)
# Clusters loop
cc_loop <- 1:24

# FEATURE LOOP
for (ff in ff_loop) {
  # DATASET LOOP
  for (dd in dd_loop) {
    # METHOD LOOP
    for (mm in mm_loop) {
      cat(paste0("#### ", feature_list[ff], " > ", dataset_list[dd], " > ", 
          method_list[mm], "\n\n"))
      # Initialization of txt_list
      txt_list <- list(img = rep("", 12), cap = rep("", 12))
      # CLUSTER LOOP
      for (cc in cc_loop) {
        # Get index
        cc_idx <- cc #(cc - 1) %% 12 + 1
        # Path to file
        card_path <- paste0(hmp_path, "hmp_", ff, dd, mm, "_", cc, "-24.png")
        # Complete txt_list
        if (file.exists(card_path)) {
          txt_list$img[cc_idx] <- paste0("![](", card_path, ")")
        } else {
          txt_list$img[cc_idx] <- no_file
        }
        txt_list$cap[cc_idx] <- paste0(
          feature_list[ff], " > ", 
          dataset_list[dd], " > ", 
          method_list[mm], " > ", 
          "#", cc, "\n\n"
        )
        # Print HTML table
        if (cc_idx == 24) {
          cat(table_of_cards(txt_list))
        }
      }
    }
  }
}

```
